Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-06-27 PaperOnSmoothing/draft-31052016.tex
Started writing on Methods section.

To construct two-dimensional probability density functions we apply non-parametric density estimation.
To make density histograms we consider a two-dimensional binned region of space, and count the number of positions that fall into each bin. For each bin location $X$, in the time interval $t$, we apply the kernel density estimation (KDE) method \cite{scott}\cite{silverman} given by

\begin{equation}
\hat{d}(X,t)=\frac{1}{N }\sum_{i=1}^{N} K_{h_{x}} (x-x_{i}) K_{h_{y}} (y-y_{i})
\label{kde}
\end{equation}

where $K_{h_{u}}$ is the kernel function $K_{h}(u)=K(u/h)/h$, $h$ is the smoothing parameter, or bandwidth, and $N$ is the number of data points (positions) in the time interval $t$.

The bandwith parameter $h$ is crucial for the accuracy of the density estimate. 
Several theoretical approaches are possible.
Here we base our choice of kernel bandwidth values $h$ on the error values $(\sigma_{x},\sigma_{y})$ provided by the positioning methods (see Section ).

>>>>

To construct two-dimensional probability density functions we apply non-parametric density estimation.
For each bin location $X$, in the time interval $t$, we apply the kernel density estimation (KDE) method \cite{scott}\cite{silverman} given by

The data provides us with a series of estimated positions, together with corresponding values for the uncertainty (see Section on Positioning).
From the estimated positions we wish to generate density histograms.

To make density estimates we consider a two-dimensional binned region of space, and count the number of positions that fall into each bin.
We wish to visualize / preserve the uncertainty for each estimated position.
Therefore we transform each bin count into a bivariate Gaussian, using the separate error values ($\sigma_{x}$ and $\sigma_{y}$) for each dimension / direction.
For each MAC we construct a two-dimensional density function that is the sum of these smooth positions.
Because the number of measurements are different for each detected MAC address (in the interval) we normalize each histogram separately.

We sum all the density histograms to create the total probability density histogram, which should ideally integrate to the number of MAC's detected (in the interval).

We smooth each position by evaluating the following function at each bin in the histogram,

\begin{equation}
\hat{d}(x,y)=K((x-x_{i}),\sigma_{x}) K((y-y_{i}),\sigma_{y})
\label{kde}
\end{equation}
where the location $(x,y)$ is expressed in bin unit, and where we use the kernel function
\begin{equation}
K(u,\sigma)=\frac{1}{\sigma\sqrt{2\pi}}\exp(\frac{u^2}{2\sigma^2})
\end{equation}
Because the distances are expressed in bin units we scale the sigma's  ($\sigma_{x}$ and $\sigma_{y}$) by dividing the error values $\epsilon$ by the bin size $h$ 
\begin{equation}
\sigma=\frac{\epsilon}{h}
\end{equation}
This implies that the bin size becomes the unit for our density estimates, and we generate probabilities for number of people per bin, which has the area $h\times h$.
